Accelerating Genetic ANN Training using the CUDA Platform

### 2010-04-18 doc/paper.tex
Remove redundant word
git-svn-id: http://svn.scesoc.ca/evolution/trunk@82 fee98b4c-d1c3-4d34-9525-a468159e4a48
Swap two paragraphs so we can use the "global memory" term later
git-svn-id: http://svn.scesoc.ca/evolution/trunk@83 fee98b4c-d1c3-4d34-9525-a468159e4a48

% ----------------------------------------------------------------------------
\subsection{The CUDA Platform} \label{cuda}
% ----------------------------------------------------------------------------
NVidia's Compute Unified Device Architecture (CUDA) is a programming paradigm for massively parallel processors present in off-the-shelf graphics cards (GPUs). GPUs consist of many independent floating-point computation units, providing significant speedup to data-parallel compute-intensive applications. Each unit is connected to on-board memory using a very wide bus, enabling very high memory bandwidth provided certain particular memory access rules are respected. The combination of these features makes CUDA an ideal platform for GA-ANN training.

The computational unit in CUDA is the "kernel", which is a C function executed in parallel on the grid of available compute units in the CUDA device. The function can request its position in this grid such that it can apply the same algorithm to values at different addresses in memory. In addition, if groups of kernels access sequential addresses in memory, the memory fetches are done in parallel, maximizing bus bandwidth utilization. This is referred to as coalesing.

@@

>>>>

% ----------------------------------------------------------------------------
\subsection{The CUDA Platform} \label{cuda}
% ----------------------------------------------------------------------------
NVidia's Compute Unified Device Architecture (CUDA) is a programming paradigm for massively parallel processors present in off-the-shelf graphics cards (GPUs). GPUs consist of many independent floating-point units, providing significant speedup to data-parallel compute-intensive applications. Each unit is connected to on-board memory using a very wide bus, enabling very high memory bandwidth provided certain particular memory access rules are respected. The combination of these features makes CUDA an ideal platform for GA-ANN training.

@@

The computational unit in CUDA is the "kernel", which is a C function executed in parallel on the grid of available compute units in the CUDA device. The function can request its position in this grid such that it can apply the same algorithm to values at different addresses in memory. In addition, if groups of kernels access sequential addresses in global memory, the memory fetches are done in parallel, maximizing bus bandwidth utilization. This is referred to as memory access coalesing.
